---
title: "TP_EX3"
author: "vhinyg"
date: "28/09/2020"
output: html_document
---

```{r}
tab = read.table("cellphonedata.txt", header = T,sep = ";",dec = ",")

X = cbind(rep(1,length(tab[,1])-2),tab[1:(length(tab[,1])-2),1]) 

```

Affichages des données

```{r}
Ytest = tab[1:(length(tab[,1])-2),c(2)]
Yfut = tab[(length(tab[,1])-1):(length(tab[,1])),c(2)]
Xtest = tab[1:(length(tab[,1])-2),c(1)]
Xfut = Yfut = tab[(length(tab[,1])-1):(length(tab[,1])),c(1)]
X1 = cbind(rep(1,length(tab[,1])-2),Xtest)
plot(Xtest,Ytest,col = 'blue4',xlab = "Year",ylab = "Number of sale",panel.first = grid(10))
```

The trend of the curve let us think that a linear model doesn't fit with data. The trend let us think about a $atan$ or an $tanh$ function between the model $\mathbf{Y}$ and the variable $\mathbf{X}$
However we are going to give a chance to the linear model then see his limitations on predictions

```{r}
cor(tab)
```
However, because  $\rho_{xy} = 0.95$ we are going to give a chance to the linear model then see his limitations on predictions. First it's to notice that this cross correlations term is close to 1 because most of data are in the middle of the distribution


\mathbf{The linear model}

Estimation de $\^{\beta}$ and $\^{Y}$
```{r}
tab1 = tab[1:(length(tab[,1])-2),]
(tab1)
modreg = lm(EndUsers ~ . , data = tab1)
summary(modreg)
betah = modreg$coefficients
betah #coefficient beta hat
Yhat = X1%*%betah

```










plot of the data estimated trend

```{r}
{plot(Xtest,Yhat,xlab = "Year",ylab = "Number of sale",panel.first = grid(10)) 
abline(betah[1],betah[2],col = 2,lty =2)
par(new = T)
plot(Xtest,Ytest,col = 'blue4',xlab = "Year",ylab = "Number of sale",panel.first = grid(10))}


{plot(Xtest,Yhat - Ytest,xlab = "Year",ylab = "misfit", col = "red",panel.first = grid(10))
abline(0,0,col = 1,lty =2)}
```
we can see how bad is the linear model, it doesn't fit to data. And the trend show that a prediction will give data far from the reality.

Exemple let's predict Year 2020 and 2021

```{r}
Xpred  = matrix(c(1,1,2020,2021),2,2)
Ypred = Xpred%*%betah
misfit = Ypred - Yfut
```
We are going to look a for a new model.



############################################################################################################
ATTENTION !!!!!!

PAS FINI!!!!!!!
We are oing to try the sigmoid function on these data
if $y = f(x)$ with $f(x) = \frac{1}{1+exp(-\lambda x)}$ We are going to estimate the best $\lambda$
The inverse of $f$ is $f^{-1}(x) =  -(1/\lambda) * ln(\frac{1}{y}-1) = \alpha * ln(\frac{1}{y}-1) $

We are going to estimate $\alpha$ through a linear regression between $x = year$  and $ln(\frac{1}{y}-1)$ avec $y = N_{sale}$

Data
```{r}
Ytestb = -log(1-(1/Ytest))
dim(tab)
Y1 = cbind(rep(1,length(Ytestb)),Ytestb)
Y1
tab2 = as.data.frame(cbind(Xtest,Ytestb))
tab2
regmod = lm(Xtest ~ ., data = tab2)
summary(regmod)

betah2 = regmod$coefficients
lambda= betah2[2]

Xhat2 = Y1 %*% betah2
Xhat2 
plot(Xhat2,Ytestb)
```

We have the $\lambda$ for the simoid function now we can build the model 

```{r}
Yhat2 = 1/(1+exp(lambda*Xhat2))
Xhat2
lambda
Yhat2
plot(Xtest,Yhat2)
```






Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
